---
title: "Advanced R Group Project"
author: 
date: "6/3/2019"
output: html_document
---

```{r setup}
source('./load_libraries.R')

raw_bank_train <- fread("Data/BankCamp_train.csv")
raw_bank_test <- fread("Data/BankCamp_test.csv")

```

## SMOTE
```{r}
fixed_train_df <- fix_types(create_weekday(raw_bank_train))

train_test <- f_partition(fixed_train_df, test_proportion=0.1, seed=20190603)

train_to_smote <- train_test$train
holdout <- train_test$test

smote_train_df <- SMOTE(y ~ ., train_to_smote, perc.over = 500)
print(summary(smote_train_df))

fwrite(smote_train_df, file = "Data/smote_train.csv")
```


## Baselines
### Logit
```{r}

if(file.exists("./saved_models/logit_baseline_smote.rds")) {
  print("Model already trained, reading from file...")
  logit_baseline_smote <- readRDS("./saved_models/logit_baseline_smote.rds")
} else {
  print("Saved model not found, starting training process...")
  pp <- c(scale_df)
  logit_baseline_smote <- pipeline_casero(smote_train_df, preprocessing=pp, model="glm")
  saveRDS(logit_baseline_smote, "./saved_models/logit_baseline_smote.rds")
}


logit_results <- evaluate_model(model=logit_baseline_smote, holdout=scale_df(holdout), "logit_baseline_smote")

model_results <- setNames(data.table(matrix(nrow = 0, ncol = 15)), names(logit_results))
model_results <- rbind(model_results, logit_results)

model_results

```


### Random Forest
```{r}
if(file.exists("./saved_models/rf_baseline_smote.rds")) {
  print("Model already trained, reading from file...")
  rf_baseline_smote <- readRDS("./saved_models/rf_baseline_smote.rds")
} else {
  print("Saved model not found, starting training process...")
  tg <- data.table(expand.grid(mtry=15,
                             splitrule='gini',
                             min.node.size=5))

  rf_baseline_smote <- pipeline_casero(smote_train_df, tunegrid=tg)
  saveRDS(rf_baseline_smote, "./saved_models/rf_baseline_smote.rds")
}

model_results <- rbind(model_results, evaluate_model(model=rf_baseline_smote, holdout=holdout, "rf_baseline_smote"))

model_results

```


### XG Boost
```{r}
if(file.exists("./saved_models/xgb_baseline_smote.rds")) {
  print("Model already trained, reading from file...")
  xgb_baseline_smote <- readRDS("./saved_models/xgb_baseline_smote.rds")
} else {
  # So many tuning parameters wow
  tg <- data.table(expand.grid(eta=0.4,
                             max_depth='2',
                             nrounds=500,
                             gamma=10,
                             colsample_bytree=0.5,
                             min_child_weight=5,
                             subsample=0.9))

  xgb_baseline_smote <- pipeline_casero(smote_train_df, model="xgbTree", tunegrid=tg)
  saveRDS(xgb_baseline_smote, "./saved_models/xgb_baseline_smote.rds")

}

model_results <- rbind(model_results, evaluate_model(model=xgb_baseline_smote, holdout=holdout, "xgb_baseline_smote"))

model_results
```

# Remove Duration

Duration is not something we would have at time of prediction, so using it is cheating. This repeats the process above but on SMOTE-d data that excludes the duration feature.

## SMOTE
```{r}
fixed_train_df <- fix_types(create_weekday(drop_duration(raw_bank_train)))

train_test <- f_partition(fixed_train_df, test_proportion=0.1, seed=20190603)

train_to_smote <- train_test$train
holdout <- train_test$test

smote_train_df <- SMOTE(y ~ ., train_to_smote, perc.over = 500)
print(summary(smote_train_df))

fwrite(smote_train_df, file = "Data/smote_train_no_duration.csv")
```


## Baselines
### Logit
```{r}

if(file.exists("./saved_models/no_duration/no_duration/logit_baseline_smote.rds")) {
  print("Model already trained, reading from file...")
  logit_baseline_smote <- readRDS("./saved_models/no_duration/logit_baseline_smote.rds")
} else {
  print("Saved model not found, starting training process...")
  pp <- c(scale_df)
  logit_baseline_smote <- pipeline_casero(smote_train_df, preprocessing=pp, model="glm")
  saveRDS(logit_baseline_smote, "./saved_models/no_duration/logit_baseline_smote.rds")
}


logit_results <- evaluate_model(model=logit_baseline_smote, holdout=scale_df(holdout), "logit_baseline_smote")

model_results <- setNames(data.table(matrix(nrow = 0, ncol = 15)), names(logit_results))
model_results <- rbind(model_results, logit_results)

model_results

```

### Random Forest
```{r}
if(file.exists("./saved_models/no_duration/rf_baseline_smote.rds")) {
  print("Model already trained, reading from file...")
  rf_baseline_smote <- readRDS("./saved_models/no_duration/rf_baseline_smote.rds")
} else {
  print("Saved model not found, starting training process...")
  tg <- data.table(expand.grid(mtry=15,
                             splitrule='gini',
                             min.node.size=5))

  rf_baseline_smote <- pipeline_casero(smote_train_df, tunegrid=tg)
  saveRDS(rf_baseline_smote, "./saved_models/no_duration/rf_baseline_smote.rds")
}

model_results <- rbind(model_results, evaluate_model(model=rf_baseline_smote, holdout=holdout, "rf_baseline_smote"))

model_results

```


### XG Boost
```{r}
if(file.exists("./saved_models/no_duration/xgb_baseline_smote.rds")) {
  print("Model already trained, reading from file...")
  xgb_baseline_smote <- readRDS("./saved_models/no_duration/xgb_baseline_smote.rds")
} else {
  # So many tuning parameters wow
  tg <- data.table(expand.grid(eta=0.4,
                             max_depth='2',
                             nrounds=500,
                             gamma=10,
                             colsample_bytree=0.5,
                             min_child_weight=5,
                             subsample=0.9))

  xgb_baseline_smote <- pipeline_casero(smote_train_df, model="xgbTree", tunegrid=tg)
  saveRDS(xgb_baseline_smote, "./saved_models/no_duration/xgb_baseline_smote.rds")

}

model_results <- rbind(model_results, evaluate_model(model=xgb_baseline_smote, holdout=holdout, "xgb_baseline_smote"))

model_results
```


### Scaling for Tree-Based Models
#### Random Forest
```{r}
if(file.exists("./saved_models/no_duration/rf_scaled.rds")) {
  print("Model already trained, reading from file...")
  rf_scaled <- readRDS("./saved_models/no_duration/rf_scaled.rds")
} else {
  print("Saved model not found, starting training process...")
  
  pp <- c(scale_df)
  
  tg <- data.table(expand.grid(mtry=15,
                             splitrule='gini',
                             min.node.size=5))

  rf_scaled <- pipeline_casero(smote_train_df, preprocessing=pp, tunegrid=tg)
  saveRDS(rf_scaled, "./saved_models/no_duration/rf_scaled.rds")
}

model_results <- rbind(model_results, evaluate_model(model=rf_scaled, holdout=scale_df(holdout), "rf_scaled"))

model_results

```


#### XG Boost
```{r}
if(file.exists("./saved_models/no_duration/xgb_scaled.rds")) {
  print("Model already trained, reading from file...")
  xgb_scaled <- readRDS("./saved_models/no_duration/xgb_scaled.rds")
} else {
  
  pp <- c(scale_df)
  
  # So many tuning parameters wow
  tg <- data.table(expand.grid(eta=0.4,
                             max_depth='2',
                             nrounds=500,
                             gamma=10,
                             colsample_bytree=0.5,
                             min_child_weight=5,
                             subsample=0.9))

  xgb_scaled <- pipeline_casero(smote_train_df, model="xgbTree", preprocessing=pp, tunegrid=tg)
  saveRDS(xgb_scaled, "./saved_models/no_duration/xgb_scaled.rds")

}

model_results <- rbind(model_results, evaluate_model(model=xgb_scaled, holdout=scale_df(holdout), "xgb_scaled"))

model_results
```


## Feature Engineering
######################################################## Logit Model ######################################################
###########################################################################################################################
###########################################################################################################################

### FE1: Drop Day
```{r}
if(file.exists("./saved_models/no_duration/logit_drop_day.rds")) {
  print("Model already trained, reading from file...")
  logit_drop_day <- readRDS("./saved_models/no_duration/logit_drop_day.rds")
} else { 
  print("Saved model not found, starting training process...")
  pp <- c(scale_df)
  fs <- c(drop_day)
  logit_drop_day <- pipeline_casero(smote_train_df, preprocessing=pp, selection=fs, model="glm")
  saveRDS(logit_drop_day, "./saved_models/no_duration/logit_drop_day.rds")
}

model_results <- rbind(model_results, evaluate_model(model=logit_drop_day, holdout=scale_df(holdout), "logit_drop_day"))

model_results

```


### FE2: Drop Pdays
```{r}
if(file.exists("./saved_models/no_duration/logit_drop_pdays.rds")) {
  print("Model already trained, reading from file...")
  logit_drop_pdays <- readRDS("./saved_models/no_duration/logit_drop_pdays.rds")
} else { 
  print("Saved model not found, starting training process...")
  pp <- c(scale_df)
  fs <- c(drop_pdays)
  logit_drop_pdays <- pipeline_casero(smote_train_df, preprocessing=pp, selection=fs, model="glm")
  saveRDS(logit_drop_pdays, "./saved_models/no_duration/logit_drop_pdays.rds")
}

model_results <- rbind(model_results,
                       evaluate_model(model=logit_drop_pdays,
                                      holdout=scale_df(holdout),
                                      "logit_drop_pdays"))

model_results
```


### FE3: Combined
```{r}
if(file.exists("./saved_models/no_duration/logit_drop_day_pdays.rds")) {
  print("Model already trained, reading from file...")
  logit_drop_day_pdays <- readRDS("./saved_models/no_duration/logit_drop_day_pdays.rds")
} else { 
  print("Saved model not found, starting training process...")
  pp <- c(scale_df)
  fs <- c(drop_day, drop_pdays)
  logit_drop_day_pdays <- pipeline_casero(smote_train_df, preprocessing=pp, selection=fs, model="glm")
  saveRDS(logit_drop_day_pdays, "./saved_models/no_duration/logit_drop_day_pdays.rds")
}

model_results <- rbind(model_results,
                       evaluate_model(model=logit_drop_day_pdays,
                                      holdout=scale_df(holdout),
                                      "logit_drop_day_pdays"))

model_results

```


###################################################### Random Forest ######################################################
###########################################################################################################################
###########################################################################################################################

### FE1: Drop Day
```{r}
if(file.exists("./saved_models/no_duration/rf_drop_day.rds")) {
  print("Model already trained, reading from file...")
  rf_drop_day <- readRDS("./saved_models/no_duration/rf_drop_day.rds")
} else {
  print("Saved model not found, starting training process...")
  tg <- data.table(expand.grid(mtry=15,
                             splitrule='gini',
                             min.node.size=5))
  
  fs <- c(drop_day)

  rf_drop_day <- pipeline_casero(smote_train_df, tunegrid=tg, selection=fs)
  saveRDS(rf_drop_day, "./saved_models/no_duration/rf_drop_day.rds")
}

model_results <- rbind(model_results, evaluate_model(model=rf_drop_day, holdout=holdout, "rf_drop_day"))

model_results
```


### FE2: Drop Pdays
```{r}
if(file.exists("./saved_models/no_duration/rf_drop_pdays.rds")) {
  print("Model already trained, reading from file...")
  rf_drop_day_pdays <- readRDS("./saved_models/no_duration/rf_drop_pdays.rds")
} else {
  print("Saved model not found, starting training process...")
  tg <- data.table(expand.grid(mtry=15,
                             splitrule='gini',
                             min.node.size=5))
  
  fs <- c(drop_pdays)

  rf_drop_pdays <- pipeline_casero(smote_train_df, tunegrid=tg, selection=fs)
  saveRDS(rf_drop_pdays, "./saved_models/no_duration/rf_drop_pdays.rds")
}

model_results <- rbind(model_results, evaluate_model(model=rf_drop_pdays, holdout=holdout, "rf_drop_pdays"))

model_results
```


### FE3: Combined
```{r}
if(file.exists("./saved_models/no_duration/rf_drop_day_pdays.rds")) {
  print("Model already trained, reading from file...")
  rf_drop_day_pdays <- readRDS("./saved_models/no_duration/rf_drop_day_pdays.rds")
} else {
  print("Saved model not found, starting training process...")
  tg <- data.table(expand.grid(mtry=15,
                             splitrule='gini',
                             min.node.size=5))
  
  fs <- c(drop_day, drop_pdays)

  rf_drop_day_pdays <- pipeline_casero(smote_train_df, tunegrid=tg, selection=fs)
  saveRDS(rf_drop_day_pdays, "./saved_models/no_duration/rf_drop_day_pdays.rds")
}

model_results <- rbind(model_results, evaluate_model(model=rf_drop_day_pdays, holdout=holdout, "rf_drop_day_pdays"))

model_results
```


### FE3: Drop Day
```{r}
if(file.exists("./saved_models/no_duration/xgb_drop_day.rds")) {
  print("Model already trained, reading from file...")
  xgb_drop_day <- readRDS("./saved_models/no_duration/xgb_drop_day.rds")
} else {
  # So many tuning parameters wow
  tg <- data.table(expand.grid(eta=0.4,
                             max_depth='2',
                             nrounds=500,
                             gamma=10,
                             colsample_bytree=0.5,
                             min_child_weight=5,
                             subsample=0.9))

  xgb_drop_day <- pipeline_casero(smote_train_df, model="xgbTree", tunegrid=tg)
  saveRDS(xgb_drop_day, "./saved_models/no_duration/xgb_drop_day.rds")

}

model_results <- rbind(model_results, evaluate_model(model=xgb_drop_day, holdout=holdout, "xgb_drop_day"))

model_results
```


######################################################## Logit Model ######################################################
###########################################################################################################################
###########################################################################################################################

### FE4: Cluster
```{r}
clustered <- clustering(df_train=smote_train_df, df_test=holdout, n_clusters=4)

if(file.exists("./saved_models/no_duration/logit_cluster.rds")) {
  print("Model already trained, reading from file...")
  logit_cluster_drop_day <- readRDS("./saved_models/no_duration/logit_cluster.rds")
} else { 
  print("Saved model not found, starting training process...")
  pp <- c(scale_df)
  
  fs <- c(drop_day)
  
  logit_cluster <- pipeline_casero(clustered$train, preprocessing=pp, selection=fs, model="glm")
  saveRDS(logit_cluster, "./saved_models/no_duration/logit_cluster.rds")
}

model_results <- rbind(model_results, evaluate_model(model=logit_cluster,
                                                     holdout=scale_df(clustered$test),
                                                     "logit_cluster"))

model_results
```


### FE5: Cluster and Drop Day
```{r}
if(file.exists("./saved_models/no_duration/logit_cluster_drop_day.rds")) {
  print("Model already trained, reading from file...")
  logit_cluster_drop_day <- readRDS("./saved_models/no_duration/logit_cluster_drop_day.rds")
} else { 
  print("Saved model not found, starting training process...")
  pp <- c(scale_df)
  
  fs <- c(drop_day)
  
  logit_cluster_drop_day <- pipeline_casero(clustered$train, preprocessing=pp, selection=fs, model="glm")
  saveRDS(logit_cluster_drop_day, "./saved_models/no_duration/logit_cluster_drop_day.rds")
}

model_results <- rbind(model_results, evaluate_model(model=logit_cluster_drop_day,
                                                     holdout=scale_df(clustered$test),
                                                     "logit_cluster_drop_day"))

model_results
```

###################################################### Random Forest ######################################################
###########################################################################################################################
###########################################################################################################################

### FE4: Cluster
```{r}
if(file.exists("./saved_models/no_duration/rf_cluster.rds")) {
  print("Model already trained, reading from file...")
  rf_cluster <- readRDS("./saved_models/no_duration/rf_cluster.rds")
} else {
  print("Saved model not found, starting training process...")
  
  tg <- data.table(expand.grid(mtry=15,
                             splitrule='gini',
                             min.node.size=5))
  
  clustered <- clustering(df_train=smote_train_df, df_test=holdout, n_clusters=4)

  rf_cluster <- pipeline_casero(clustered$train, tunegrid=tg)
  saveRDS(rf_cluster, "./saved_models/no_duration/rf_cluster.rds")
}

model_results <- rbind(model_results, evaluate_model(model=rf_cluster, holdout=clustered$test, "rf_cluster"))

model_results
```


### FE5: Cluster and Drop Day
```{r}
if(file.exists("./saved_models/no_duration/rf_drop_day_cluster.rds")) {
  print("Model already trained, reading from file...")
  rf_drop_day_cluster <- readRDS("./saved_models/no_duration/rf_drop_day_cluster.rds")
} else {
  print("Saved model not found, starting training process...")
  
  pp<-c(drop_day)
  
  tg <- data.table(expand.grid(mtry=15,
                             splitrule='gini',
                             min.node.size=5))

  rf_drop_day_cluster <- pipeline_casero(clustered$train, tunegrid=tg, preprocessing=pp)
  saveRDS(rf_drop_day_cluster, "./saved_models/no_duration/rf_drop_day_cluster.rds")
}

model_results <- rbind(model_results, evaluate_model(model=rf_drop_day_cluster, holdout=clustered$test, "rf_drop_day_cluster"))

model_results
```


## Hyperparameter Tuning
### Random Forest
```{r}

if(file.exists("./saved_models/no_duration/rf_tuned.rds")) {
  print("Model already trained, reading from file...")
  rf_tuned <- readRDS("./saved_models/no_duration/rf_tuned.rds")
} else {
  print("Saved model not found, starting training process...")
  tg_RF <- data.table(expand.grid(mtry = c(5, 10, 15),
                                splitrule=c("gini", "extratrees"),
                                min.node.size = c(1, 5, 10)))
                    
  rf_tuned <- pipeline_casero(smote_train_df, tunegrid=tg_RF)

  saveRDS(rf_tuned, "./saved_models/no_duration/rf_tuned.rds")
}

model_results <- rbind(model_results, evaluate_model(model=rf_tuned, holdout=holdout, "rf_tuned"))

model_results
```

# Write results to a CSV
```{r}
fwrite(model_results, "./Data/model_results_no_duration.csv")
fread("./Data/model_results_no_duration.csv")
```